### 2019-01-03 manuscript/manuscript.rmd
updated R code for new files, tweaked nexus formatting for consistency

		base_name = sub( "\\.phy$", "", phylip_file )
		elements = strsplit(base_name, "_") %>% unlist()
		manuscript_name = elements[1]
		matrix_name = paste(elements[2:length(elements)], collapse="_")

@@

names(sequences_all_txt) = c("full_name")
sequences_all = str_split_fixed( sequences_all_txt$full_name, ":", 5 ) %>% 
	as_tibble()
names( sequences_all ) = c( "manuscript", "matrix", "species", "ncbi_taxon_id", "partition" )

partitions_all = 
	sequences_all %>% 
	group_by( manuscript, matrix, partition ) %>% 
	summarise( n_sequences =n() )

@@

Bs = 
	str_split_fixed( busco_results$Sequence, ":", 5 ) %>% 
	as_tibble()

names( Bs ) = c( "manuscript", "matrix", "species", "ncbi_taxon_id", "partition" )

@@

# Find overrepresented partitions, ie partitions with genes that hit more than one Busco
busco_distinct =  busco_results %>% select( manuscript, matrix, partition, Description ) %>% distinct(  )
busco_overrepresented = busco_distinct %>% group_by( manuscript, matrix, partition ) %>% summarise( n = n() ) %>% filter( n > 1 )
busco_overrepresented
busco_overrepresented_full = left_join( busco_overrepresented, busco_results )

# Combine and summarize results
partition_to_busco_map = 
	busco_distinct %>% 
	group_by( manuscript, matrix, partition ) %>% 
	summarise( BUSCO=names(which(table(Description) == max(table(Description)))[1]) )

partition_map_global %<>% left_join( partition_to_busco_map, by=c("manuscript", "matrix", "partition") )

busco_summary = 
	partition_to_busco_map %>% 
	group_by( manuscript, matrix ) %>%
	summarise( n_busco_partitions = n() )

matrix_summary =
	partitions_all %>%
	group_by( manuscript, matrix ) %>%
	summarise( n_partitions = n() ) %>%
	left_join(
		busco_summary,
		by=c("manuscript", "matrix")
	)

>>>>

		base_name = sub( "\\.phy$", "", phylip_file )
		elements = strsplit(base_name, "_") %>% unlist()
		manuscript_name = elements[1]
		matrix_name = base_name

@@

names(sequences_all_txt) = c("full_name")
sequences_all = str_split_fixed( sequences_all_txt$full_name, ":", 4 ) %>% 
	as_tibble()
names( sequences_all ) = c( "matrix", "species", "ncbi_taxon_id", "partition" )

partitions_all = 
	sequences_all %>% 
	group_by( matrix, partition ) %>% 
	summarise( n_sequences =n() )

@@

Bs = 
	str_split_fixed( busco_results$Sequence, ":", 4 ) %>% 
	as_tibble()

names( Bs ) = c( "matrix", "species", "ncbi_taxon_id", "partition" )

@@

# Find overrepresented partitions, ie partitions with genes that hit more than one Busco
busco_distinct =  busco_results %>% select( matrix, partition, Description ) %>% distinct(  )
busco_overrepresented = busco_distinct %>% group_by( matrix, partition ) %>% summarise( n = n() ) %>% filter( n > 1 )
busco_overrepresented
busco_overrepresented_full = left_join( busco_overrepresented, busco_results )

# Combine and summarize results
partition_to_busco_map = 
	busco_distinct %>% 
	group_by( matrix, partition ) %>% 
	summarise( BUSCO=names(which(table(Description) == max(table(Description)))[1]) )

partition_map_global %<>% left_join( partition_to_busco_map, by=c("matrix", "partition") )

busco_summary = 
	partition_to_busco_map %>% 
	group_by( matrix ) %>%
	summarise( n_busco_partitions = n() )

matrix_summary =
	partitions_all %>%
	group_by( matrix ) %>%
	summarise( n_partitions = n() ) %>%
	left_join(
		busco_summary,
		by=c("matrix")
	)

matrix_summary$manuscript = str_split( matrix_summary$matrix, "_", simplify=TRUE )[,1]
